Evaluate PEER in each cohort and brain region

### 2021-02-24 combined_analysis/eval_resid_in_each.Rmd
add more summary info

@@

@@

```{r cache=FALSE}
knitr::knit_exit()
```

@@

# formula used to fit model
form.lst = list(
  `MSSM-Penn-Pitt`  = ~ Dx + Reported_Gender + RIN +scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + Institution*(ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3),
  `NIMH-HBCC`       = ~ Dx + Reported_Gender + RIN + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3)

@@

  `MSSM-Penn-Pitt`  = ~ Dx + Reported_Gender + RIN +scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + Institution*(ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3)

  `NIMH-HBCC`       = ~ Dx + Reported_Gender + RIN + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3

>>>>

# Ethnicity
# Genotype_Inferred_Ancestry
# Race

@@

```{r ancestry}
fig1 = ggplot(ANCESTRY.MPP, aes(EV.1, EV.2, color=Cluster)) + geom_point() + ggtitle("MPP ancestry")  + theme(aspect.ratio=1)
fig2 = ggplot(ANCESTRY.HBCC, aes(EV.1, EV.2, color=as.character(cluster))) + geom_point() + ggtitle("HBCC ancestry")  + theme(aspect.ratio=1)
fig3 = ggplot(ANCESTRY.HBCC, aes(EV.1, EV.2, color=Population)) + geom_point() + ggtitle("HBCC ancestry") + theme(aspect.ratio=1)
plot_grid(fig1, fig2, fig3, nrow=1)
```

@@

@@

# formula used to fit model
form.lst = list(
  `MSSM-Penn-Pitt`  = ~ Dx + Reported_Gender + RIN +scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + Institution*(ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3 + EV.1 + EV.2 + EV.3 + EV.4 + EV.5),
  `NIMH-HBCC`       = ~ Dx + Reported_Gender + RIN + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3 + EV.1 + EV.2 + EV.3 + EV.4 + EV.5)

@@

`MSSM-Penn-Pitt`  = ~ Dx + Reported_Gender + RIN +scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + Institution*(ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3) + EV.1 + EV.2 + EV.3 + EV.4 + EV.5

`NIMH-HBCC`       = ~ Dx + Reported_Gender + RIN + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3 + EV.1 + EV.2 + EV.3 + EV.4 + EV.5
